Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-01-23 ms.rmd
Sort of fixed image

@@

```{r, fig2,  eval = TRUE, fig.cap="Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems"}

@@

fig2 <- (ptm + ptf + ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
fig2
ggsave(fig2, filename = "./output/figures/fig2_trait.pdf", height = 10, width = 40, device = "pdf", limitsize = FALSE, units = "cm")
```

>>>>

The magnitude of difference in $lnRR_{Q_{10}}_{acclimation}$ and $lnRR_{Q_{10}}_{acute}$ was very small (). Considering acute responses of acclimated animals at high temperatures are also expected to increase (see above), acclimatization is not likely going to provide adaptive benefits under climate change.

@@

```{r, fig2, out.width = "100%", eval = TRUE, fig.cap="Acute and Acclimation lnRR q10 across traits for A) marine, B) freshwater and C) terrestrial systems"}

@@

fig2 <- (ptm + ptf + ptt) + plot_annotation(tag_levels = "A", tag_suffix = ")")
ggsave(fig2, filename = "./output/figures/fig2_trait.pdf", height = 10, width = 40, device = "pdf", limitsize = FALSE, units = "cm")

img_fig2 <- magick::image_read("./output/figures/fig2_trait.pdf")
img_fig2
```
